Draft Visualizations for Semester Project

### 2018-12-01 Visualizations/Draft Visualizations Template.Rmd
Final change
Commit

@@

###Percentage of employers who have a formal discussion about mental health with their employees

>>>>

###Distribution of mental health disorder based on geography

```{r}
table(health$What.US.state.or.territory.do.you.live.in. , health$Do.you.currently.have.a.mental.health.disorder.)
```

From the above table output, we can see that the US state with the majority of mental health illness cases is California, followed by Illoinois and New York

@@

####Percentage of employers who have a formal discussion about mental health with their employees
